\documentclass[a4paper,10pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\renewcommand{\familydefault}{\sfdefault}
\pagestyle{empty}

\usepackage[none]{hyphenat}

\usepackage[scaled=0.85]{helvet}

\begin{document}

\begin{center}
    {\LARGE \textbf{Ariel Noyman, PhD}} \\
    \href{mailto:noyman@mit.edu}{noyman@mit.edu} \,|\, \href{http://arielnoyman.com}{arielnoyman.com} \,|\, New York, NY \\
    \href{https://www.linkedin.com/in/arielnoyman}{linkedin.com/in/arielnoyman}
\end{center}


\vspace{2em}

\noindent \textbf{Profile} \\
Urban scientist and innovation leader with 10+ years’ experience advancing sustainable and inclusive urban development through public-private partnerships. Expert in coalition building, data-driven planning, and entrepreneurship support, with deep ties to civic, academic, and startup ecosystems in the US, EU, the Middle-East, and Asia. Proven track record in leading urban innovation and design projects, securing funding, and fostering cross-sector collaboration to drive impactful change in cities.



\vspace{2em}

\noindent \textbf{Experience}

\begin{itemize}[leftmargin=1.2em]
    \item \textbf{Research Scientist, City Science Group} — MIT Media Lab, Cambridge, MA (2015–Present) \\
          Lead strategy and partnerships for global and Boston-based urban innovation projects. Established Negev Urban Research Lab (secured \$2.5M funding) and coordinated \$5M+ for Hamburg CityScience Lab. Developed CityScope, deployed globally for resilience, mobility, and civic engagement. Supported Boston BRT planning via participatory tech.

    \item \textbf{Adjunct Professor \& Mentor} — MIT, Cornell Tech, Northeastern (2015–Present) \\
          Taught and mentored urban tech entrepreneurs; developed courses on civic tech, innovation ecosystems, and urban transformation.

    \item \textbf{Data Scientist (Residency)} — Autodesk, Boston, MA (2021) \\
          Applied predictive analytics to infrastructure and urban design.

    \item \textbf{Founding Member} — Urban AI (global) (2019) \\
          Helped establish \textit{Urban AI}, a global network of urban innovation leaders. Mentored, instructed, and supported startups and initiatives in urban tech.

    \item \textbf{Project Manager \& Architect} — Various Firms (NYC, Tel Aviv, EU) (2006–2012) \\
          Directed complex urban development and civic projects across sectors.
\end{itemize}

\vspace{2em}

\noindent \textbf{Key Achievements}
\begin{itemize}[leftmargin=1.2em]
    \item Founded/expanded \textbf{City Science Living Labs} in Boston, Hamburg, Andorra, Shanghai, and Helsinki.
    \item Directed \textbf{Finding Places (Hamburg)}, a participatory urban planning platform (OPSI-European Commission Award).
    \item Featured by \emph{The New York Times, The Guardian, Wired, 60 Minutes} for leadership in urban innovation.
    \item Recognized by \textbf{OECD, European Commission, and national governments} for impact on urban innovation, design, and civic engagement.
\end{itemize}

\vspace{0.5em}

\noindent \textbf{Education}
\begin{itemize}[leftmargin=1.2em]
    \item PhD — Massachusetts Institute of Technology (\textit{CityScope: Urban Modeling \& Simulation}, 2022)
    \item MSc, Urbanism — Massachusetts Institute of Technology (2015)
    \item BArch (Cum Laude) — Bezalel Academy of Arts and Design, Jerusalem (2008)
\end{itemize}

\vspace{2em}

\noindent \textbf{Skills} \\
Project \& Stakeholder Management \,|\, Urban Innovation Ecosystems \,|\, Public-Private Partnerships \,|\, Fundraising \& Strategy \,|\, Data-Driven Urbanism \,|\, Civic Engagement Platforms \,|\, Communication \& Storytelling

\end{document}
