\section*{Projects}
Selected work in urban science, architecture and urban design. For a complete list of projects, please see the \textbf{Projects} section of my website and portfolio: \href{https://arielnoyman.com/}{https://arielnoyman.com/}

\subsection*{MIT Media Lab}

\begin{tablist}

    \item[2015-present] \tab \textbf{City Science Network:} {Helped establish a global network of City Science Labs, including Andorra (2015), Hamburg (2015), Helsinki (2017), Shanghai (2017), Detroit (2019), Ho Chi Minh City (2020), and the Negev (2022).}

    \begin{tablist}
        \item[2022-present] \tab  {\textbf{Negev Urban Research (NUR)}, an MIT/Israeli Government urban science lab in the Negev region. Initiated the lab, assembled the team, and secured +\$2.5M in government funding.}
    \end{tablist}

    \begin{tablist}
        \item[2015-present] \tab  {\textbf{HCU CityScience Lab} in Hamburg, Germany - a multi-year cooperation agreement between MIT, the Free and Hanseatic City of Hamburg, and HafenCity Universität Hamburg. Coordinated MIT-HCU research and projects; helped secure +5M EUR in funding.}
    \end{tablist}




    \item[2014-present] \tab \textbf{MIT CityScope} {An urban modeling, simulation, and decision-making platform developed at the MIT City Science Center and deployed internationally.}

    \begin{tablist}
        \item[2016] \tab \href{https://obamawhitehouse.archives.gov/blog/2016/02/23/pcast-releases-technology-and-future-cities-report-president}{President Obama Council of Advisors on Science and Technology (PCAST), Technology and the Future of Cities Report, p. 24}
    \end{tablist}

    \item[2015-2016] \tab \textbf{CityScope FindingPlaces} {HCI platform for public participation in refugees' accommodation planning process.}

    \begin{tablist}

        \item[2019] \tab \href{https://www.youtube.com/watch?v=PZg6A_A65lQ}{FindingPlaces \& CityScienceLab at the “City Science Summit”, Hamburg, Germany}

        \item[2016] \tab  \href{https://medium.com/mit-media-lab/shifting-priorities-finding-places-9ad3bdbe38b8}{Shifting Priorities, Finding Places | by MIT Media Lab}

        \item[2017] \tab \href{https://www.media.mit.edu/publications/finding-places/}{Finding Places: HCI Platform for Public Participation in Refugees’ Accommodation Process}

        \item[2018] \tab  \href{https://datasmart.ash.harvard.edu/news/article/ar-transforming-tech-what-can-it-do-cities}{AR Is Transforming Tech. What Can It Do for Cities?}

    \end{tablist}


    \item[2014-2015] \tab \textbf{CityScope BRT For Boston} {Interactive urban planning platform for participatory transit design.}

    \begin{tablist}

        \item[2015] \tab  \href{https://www.bloomberg.com/news/articles/2015-10-16/mit-s-new-interactive-lego-urban-tool-brings-transparency-to-transit-planning}
        {MIT's New Interactive LEGO Urban Tool Brings Transparency to Transit Planning}

        \item[2015] \tab  \href{http://www.brt.cl/new-tools-for-a-new-era-of-open-transportation-planning/}
        {Centre of Excellence}

        \item[2016] \tab  \href{https://www.media.mit.edu/projects/CityscopeBostonBRT/overview/}
        {Boston Bus Rapid Transit (BRT) Community Engagement}

        \item[2016] \tab  \href{http://www.bostonbrt.org/mit-nuestra-comunidad-brt-lego-workshops}
        {MIT + Nuestra Comunidad BRT LEGO Workshops, Boston BRT}

    \end{tablist}

    \item[2018-2021] \tab \textbf{CityScope Grasbrook} {Multi-participant platform for design collaboration and evaluation of proposals for HCH and Herzog de Meuron (HdM).}

    \item[2024-2026] \tab \textbf{The Right to Shelter} {Spatial analysis and collaborative planning tools for expanding bomb-shelter access in marginalized communities using spatial data analysis and machine learning methods.}

    \begin{tablist}
        \item[2025] \tab \href{https://www.ynetnews.com/real-estate/article/s1zbwjtyxx}{``Innovative algorithm aims to protect Negev Bedouin villages from missile attacks''}
    \end{tablist}




\end{tablist}


\subsection*{MIT Center For Advanced Urbanism}



\begin{tablist}

    \item[2013-2014] \tab \textbf{Rebuild by Design (RBD)}
    {‘The New Meadowlands’: Winning entry for \$150M HUD multistage planning and design competition following hurricane Sandy in the Tri-State area}
\end{tablist}


\subsection*{Design Projects}


\begin{tablist}

    \item[2010] \tab \textbf{The Museum Of Tolerance, Jerusalem, Israel} with Chyutin Architects. Winning entry for an international competition and design towards construction of a \$260M campus, including two museum exhibitions, a children's museum, conference center, a 500-seat banquet hall, an 800-seat lecture hall, a 1000-seat outdoor amphitheater and two viewing theaters

    \item[2011] \tab \textbf{National Institute for Biotechnology} with Chyutin Architects. National Institute for Biotechnology, Ben-Gurion University, Beer-Sheva, Israel. \$22M academic biotechnology laboratory building. Won 2018 National Design Award, Israel.

    \item[2009] \tab \textbf{The Israeli Museum, Jerusalem} with EK-A.

    \begin{tablist}
        \item[\textit{EK-A}] \href{http://www.efrat-kowalsky.co.il/project/test/}{\enquote{Israel Museum, Jerusalem, Israel}}

        \item[\textit{Archdaily}] \href {https://www.archdaily.com/373684/israel-museum-james-carpenter-design-associates}{\enquote{The Israeli Museum, Jerusalem}}
    \end{tablist}

    \item[2008] \tab \textbf{Tel-Aviv City Museum (Beit Hai'r)} A 5000 sqft city museum and a cultural center in Tel-Aviv’s old City-Hall building

    \item[2008] \tab \textbf{Ordos100, inner Mongolia, China} with EK-A.

    \begin{tablist}
        \item[\textit{New York Times}] \href{https://www.nytimes.com/2008/05/01/garden/01mongolia.html}{\enquote{In Inner Mongolia, Pushing Architecture's Outer Limits}}

        \item[\textit{CNN}] \href{https://www.cnn.com/style/article/china-ordos-ghost-town/index.html}{\enquote{Ordos, the abandoned city that's an architectural marvel}}

        \item[\textit{Archdaily}] \href{https://www.archdaily.com/32535/ordos-100-45-efrat-kowalsky-architects}{\enquote{ORDOS 100 \#45: Efrat‐Kowalsky Architects}}

        \item[\textit{Vancouver Biennale}]
        \href{https://vimeo.com/136530514}{\enquote{Ordos 100}}
    \end{tablist}

\end{tablist}