\section*{Publications}

\subsection*{Journal Articles and Conference Proceedings}

\begin{tablist}

    \item[`21] \tab
    Ronan Doorley, Alex Berke, Ariel Noyman, Luis Alonso, Josep Ribó, Vanessa Arroyo, Marc Pons, Kent Larson,
    \textit{Mobility and COVID-19 in Andorra: Country-scale analysis of high-resolution mobility patterns and infection spread}
    medRxiv 2021.02.18.21251977; doi: https://doi.org/10.1101/2021.02.18.21251977


    \item[`21] \tab
    Baeza, Jesús López, Julia L. Sievert, André Landwehr, Jonas Luft, Philipp Preuner, Jürgen Bruns-Berentelg, Ariel Noyman, and Joerg Rainer Noennig. \textit{"CityScope Platform for Real-Time Analysis and Decision-Support in Urban Design Competitions."} International Journal of E-Planning Research (IJEPR) 10, no. 4 (2021): 1-17.


    \item[`20] \tab  Noyman, A., \& Larson, K.
    \textit{DeepScope: HCI Platform for Generative Cityscape Visualization
    }
    In Extended Abstracts of the 2020 CHI Conference on Human Factors in Computing Systems (pp. 1–9)

    \item[`20] \tab  Noyman, A., \& Larson, K.
    \textit{A Deep Image of the City: Generative Urban-Design Visualization
    }
    In Proceedings of the Symposium on Simulation for Architecture and Urban Design (SimAUD 2020)


    \item[`19] \tab  Doorley, R., Noyman, A., Sakai, Y., \& Larson, K.
    What’s your MoCho? Real-time Mode Choice Prediction Using Discrete Choice Models and a HCI Platform
    In KDD 2019 UrbComp.

    \item[`19] \tab  Doorley, R. and Noyman, A., Xiong, Z., Alonso, L., Grignard, A., \& Larson, K.
    \textit{RevUrb: Understanding Urban Activity and Human Dynamics through Point Process Modelling of Telecoms Data}
    In Smart Cities Symposium Prague 2019.

    \item[`19] \tab  Noyman, A., Doorley, R., Xiong, L., Grignard, A., \& Larson, K.
    \textit{Reversed Urbanism: Inferring Urban Performance Through Behavioral Patterns In Temporal Telecom Data}
    Environment and Planning B: Urban Analytics and City Science, 46(8), 1480–1498

    \item[`18] \tab  Grignard, A., Macia, N., Alonso Pastor, L., Noyman, A., Zhang, Y., \& Larson, K.
    \textit{Cityscope andorra: A multi-level interactive and tangible agent-based visualization}
    In Proceedings of the 17th International Conference on Autonomous Agents and MultiAgent Systems (pp. 1939–1940).

    \item[`18] \tab  Alonso, L., Zhang, Y., Grignard, A., Noyman, A., Sakai, Y., ElKatsha, M., Doorley, R., \& Larson, K.
    \textit{CityScope: a data-driven interactive simulation tool for urban design. Use case volpe}
    In International Conference on Complex Systems (pp. 253–261).

    \item[`18] \tab  Noyman, A., Sakai, Y., \& Larson, K.
    \textit{CityScopeAR: urban design and crowd-sourced engagement platform
    }In CHI 2018 CHI Conference on Human Factors in Computing Systems
    \item[`17] \tab  Ariel Noyman, et al
    \textit{Finding Places: HCI Platform for Public Participation in Refugees’ Accommodation Process}
    In Knowledge-Based and Intelligent Information \& Engineering Systems: Proceedings of the 21st International Conference, KES-20176-8 September 2017, Marseille, France (pp. 2463–2472).

    \item[`17] \tab  Noyman, A., Stibe, A., \& Larson, K.
    Roadmap for autonomous cities: Sustainable transformation of urban spaces
    Americas Conference on Information Systems (AMCIS)At: Boston, MA, USA

    \item[`16] \tab  Noyman, A., Stibe, A., \& Larson, K.
    Autonomous Cities and the Urbanism of the 4th Machine Age: Should AV Industry Design Future Cities
    Changing Places Research Group, MIT Media Lab, accessed March, 29, 2017.

    \item[`15] \tab  Alrashed, T., Almalki, A., Aldawood, S., Alhindi, T., Winder, I., Noyman, A., Alfaris, A., \& Alwabil, A.
    An observational study of usability in collaborative tangible interfaces for complex planning systems
    Procedia Manufacturing, 3, 1974–1980.

    \item[`15] \tab  Noyman, A.
    Power/Structures: the Urban Form of Regulations
    Massachusetts Institute of Technology

\end{tablist}


\subsection*{Book Chapters}

\begin{tablist}
    \item[`21] \tab HafenCity University Hamburg [HCU] and the foundation ZEIT-Stiftung Ebelin und Gerd Bucerius, \textit{Perspectives in Metropolitan Research}
    \href{https://www.jovis.de/en/books/series/perspectives-in-metropolitan-research.html}{JOVIS}

    \item[`21] \tab Raphel Schwegmann / Gesa Ziemer / Jörg Rainer Noennig (Hg.), \textit{Digital City Science. Researching New Technologies in Urban Environments}
    \href{https://www.jovis.de/de/buecher/details/product/digital-city-science-researching-new-technologies-in-urban-environments.html}{JOVIS}

    \item[`20] \tab Hubert Beroche, \textit{Urban AI}
    \href{https://urban-ai.co/wp-content/uploads/2020/06/URBAN-AI-1.pdf}{https://urban-ai.co}

    \item[`18] \tab Rafi Segal, \textit{Space Packed: The Architecture of Alfred Neumann}
    \href{https://www.amazon.com/Space-Packed-Architecture-Alfred-Neumann/dp/3038600555}{ISBN 9783038600558, 3038600555}


    \item[`18] \tab José Pinto Duarte, \textit{Mass Customization and Design Democratization},
    \href{https://www.google.com/books/edition/_/Z6h8DwAAQBAJ?hl=en&gbpv=0}{ISBN 9781351117845}


    \item[`15] \tab MIT CAU + ZUS + URBANISTEN with Deltares, 75B, and Volker Infra Design, \textit{New Meadowlands: Productive city + Regional park}
    \href{http://www.rebuildbydesign.org/our-work/all-proposals/winning-projects/nj-meadowlands}{http://www.rebuildbydesign.org/}

    \item[`10] \tab \textit{What Can We Learn from China? City/state Unit Moving Cities},
    \href{https://movingcities.org/movingmemos/the-chinese-city-lecture-workshop/}{ISBN 9789659130405}


\end{tablist}

