\section*{About}

 {
  Dr. Ariel Noyman is an architect, urban designer, and an urban scientist with two decades of experience in architectural and urban design practice, urban science research, and teaching. His work explores how design and technology can~\textbf{democratize data-driven urban processes}. At MIT, Dr. Noyman developed CityScope, an Urban Human-Computer Interaction platform that integrates urban analytics and real-time simulation to create evidence-based, participatory design processes. CityScope has been deployed in over twenty cities worldwide to address challenges such as allocating refugee housing in Hamburg, enabling resident-led transit design in Boston, and aiding urban recovery efforts in war-stricken Kharkiv. To scale this research, Noyman helped establish a global network of City Science Labs that serve as living testbeds for urban innovation and participatory processes.
  Noyman's design and research work has received international recognition, including a European Union UrbanAct Award for ``FindingPlaces''; First-place award in the ``Rebuild by Design'' competition for post-hurricane recovery efforts; and first-place in the design competition for the Museum of Tolerance in Jerusalem. He has taught design studios and urban technology seminars at MIT, Cornell University, and Northeastern University. Noyman holds a PhD and SM from the Massachusetts Institute of Technology and a B.Arch (cum laude) from Bezalel Academy.
 }

\subsection*{Research Areas}
\textit{Democratizing Urban Processes:} Data-driven approaches to understanding, designing, and collaboratively planning.
\\
\textit{Urban Modeling and Simulation:} Developing urban simulation methods focusing on behavior and experience.
\\
\textit{City Science Living-Labs:} Developing a global network of urban research labs.