\documentclass[a4paper,10pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\renewcommand{\familydefault}{\sfdefault}
\pagestyle{empty}

\usepackage[none]{hyphenat}

\usepackage[scaled=0.85]{helvet}

\begin{document}

\begin{center}
      {\LARGE \textbf{Ariel Noyman, PhD}} \\
      \href{mailto:noyman@mit.edu}{noyman@mit.edu} \,|\, \href{http://arielnoyman.com}{arielnoyman.com} \,|\, Cambridge, MA \\
      \href{https://www.linkedin.com/in/arielnoyman}{linkedin.com/in/arielnoyman}
\end{center}


\vspace{2em}

\noindent \textbf{Profile} \\
Urban scientist, architect, and innovation leader with 10+ years of experience advancing data-driven and participatory urban development. Developed and deployed CityScope across 20+ cities worldwide and helped establish the global City Science Network. Proven track record in leading interdisciplinary urban innovation projects, securing multi-million-dollar funding, and building cross-sector partnerships across the US, EU, Middle East, and Asia.



\vspace{2em}

\noindent \textbf{Experience}

\begin{itemize}[leftmargin=1.2em]
      \item \textbf{Research Scientist, City Science Center} — MIT Media Lab, Cambridge, MA (2015--2017, 2022--present) \\
            Led strategy and partnerships for global and Boston-based urban innovation projects. Initiated Negev Urban Research (secured +\$2.5M in government funding) and coordinated MIT-HCU projects in Hamburg (helped secure +5M EUR).

      \item \textbf{Adjunct Professor} — Cornell Tech, Cornell University, New York, NY (2023--present) \\
            Designed and taught INFO-5420 Street Knowledge courses on urban processes, methods, and rehabilitation.

      \item \textbf{Adjunct Professor} — Northeastern University, Boston, MA (2015--2017) \\
            Taught graduate and undergraduate architecture studios on infrastructure, city systems, and thesis design.

      \item \textbf{Data Scientist (Residency)} — Autodesk, Boston, MA (2021) \\
            Contributed predictive analytics workflows for architecture and urban design applications.

      \item \textbf{Founding Member} — Urban AI, Paris (2019--present) \\
            Helped establish \textit{Urban AI}, a global network of urban innovation leaders. Mentored, instructed, and supported startups and initiatives in urban tech.

      \item \textbf{Founder \& Designer} — AN Studio, Tel-Aviv \& Geneva (2006--2013) \\
            Independent design practice focused on residential and public projects, including award-winning designs and international competitions.

      \item \textbf{Project Manager, Architecture} — Chyutin Architects, Tel-Aviv (2010--2012); EKA Architects, Tel-Aviv (2008--2009); Margalith Architects, Jerusalem (2006--2008)

      \item \textbf{Architect} (Internship) — Kohn Pedersen Fox Associates, New York, NY (2014)
\end{itemize}

\vspace{2em}

\noindent \textbf{Key Achievements}
\begin{itemize}[leftmargin=1.2em]
      \item Helped establish the \textbf{City Science Network} across Andorra, Hamburg, Helsinki, Shanghai, Detroit, Ho Chi Minh City, and the Negev.
      \item Developed \textbf{MIT CityScope}, an urban modeling and simulation platform deployed internationally for participatory planning.
      \item Led \textbf{FindingPlaces (Hamburg)}, which received a European Union UrbanAct Award (GOOD PRACTICE).
      \item Contributed to \textbf{New Meadowlands}, the winning Rebuild by Design proposal linked to \$150M in HUD-supported implementation.
      \item Featured by \emph{The New York Times, The Guardian, Wired, 60 Minutes} for leadership in urban innovation.
\end{itemize}

\vspace{0.5em}

\noindent \textbf{Education}
\begin{itemize}[leftmargin=1.2em]
      \item Ph.D. — Massachusetts Institute of Technology (\textit{CityScope: An Urban Modeling and Simulation Platform}, 2022)
      \item M.S., Architecture Studies (SMarchS) — Massachusetts Institute of Technology (2015)
      \item B.Arch (Cum Laude) — Bezalel Academy of Arts and Design, Jerusalem (2008)
\end{itemize}



\end{document}
